Modelling BCG vaccination in the UK

### 2019-08-08 rmds/05-evidence-policy-change.Rmd
further thesis tweaks
wordcount

## Read formated results
## See https://github.com/seabbs/AssessBCGPolicyChange/blob/master/vignettes/paper.Rmd
## for code required to reproduce 
## Chapter is an edited version of the orginal reproducible document.
## Original results found at: https://github.com/seabbs/AssessBCGPolicyChange/blob/master/vignettes/results/paper
## Original figures found at: https://github.com/seabbs/AssessBCGPolicyChange/blob/master/docs/articles/paper_files/figure-html
##Wordcount: 4274

@@

For each scenario, I ran the model until 2028 with 10,000 parameter samples. I tested the difference between scenarios using the Mann-Whitney test for both the number of vaccines needed to prevent a single case in 15 years after vaccination for a cohort aged 13-14 years old at vaccination and the total number of additional notifications caused by ending the BCG schools scheme. As in [@Sutherland1989] a 15 year time horizon was used with 5 year intervals. The year closest to the year of the change in vaccination policy (2005), which had model estimates, was used as the baseline. The code for this analysis is available online.^[Code: https://github.com/seabbs/AssessBCGPolicyChange]

>>>>

## Read formated results
## See https://github.com/seabbs/AssessBCGPolicyChange/blob/master/vignettes/paper.Rmd
## for code required to reproduce 
## Chapter is an edited version of the orginal reproducible document.
## Original results found at: https://github.com/seabbs/AssessBCGPolicyChange/blob/master/vignettes/results/paper
## Original figures found at: https://github.com/seabbs/AssessBCGPolicyChange/blob/master/docs/articles/paper_files/figure-html
##Wordcount: 4537

@@

For each scenario, I ran the model until 2028 with 10,000 parameter samples. I tested the difference between scenarios using the Mann-Whitney test for both the number of vaccines needed to prevent a single case in 15 years after vaccination for a cohort aged 13-14 years old at vaccination and the total number of additional notifications caused by ending the BCG schools scheme. As in [@Sutherland1989] a 15 year time horizon was used with 5 year intervals. The year closest to the year of the change in vaccination policy (2005), which had model estimates, was used as the baseline. The code for this analysis is available online^[Code: https://github.com/seabbs/AssessBCGPolicyChange].

### 2019-08-08 rmds/08-model-development.Rmd
wordcount

## Wordcount: 11105
##packages
library(tidyverse)
library(kableExtra)
library(pander)
## Resources path
resources_path <- file.path("chapters", "model-development")

>>>>

## Wordcount: 11089
##packages
library(tidyverse)
library(kableExtra)
library(pander)
## Resources path
resources_path <- file.path("chapters", "model-development")

### 2019-08-08 rmds/09-model-fitting.Rmd
wordcount

## Wordcount: 9283
##packages
library(tidyverse)
library(purrr)
library(kableExtra)
library(pander)
library(fs)
## Resources path
resources_path <- file.path("chapters", "model-fitting")

>>>>

## Wordcount: 9299
##packages
library(tidyverse)
library(purrr)
library(kableExtra)
library(pander)
library(fs)
## Resources path
resources_path <- file.path("chapters", "model-fitting")

### 2019-08-08 rmds/index.Rmd
wordcount

---
author: 'Samuel Abbott'
date: 'August 2019'
division: 'Bristol Medical School\: Population Health Sciences'
advisor: 'Ellen Brooks Pollock'
altadvisor: 'Hannah Christensen'
department: 'Faculty of Health Sciences'
title: 'Modelling BCG vaccination in the UK'
subtitle: 'What is the impact of changing policy?'
wordcount: "55,024"
knit: "bookdown::render_book"
site: "bookdown::bookdown_site"
always_allow_html: yes
output: 
  ##Thesis can only be fully built for pdf using the makefile
  #thesisdown::thesis_pdf: default
  thesisdown::thesis_gitbook: default
  #thesisdown::thesis_word: default
  #thesisdown::thesis_epub: default
bibliography: ["bib/thesis.bib"]
#Download your specific bibliography database file and refer to it in the line above.
link-citations: yes
colorlinks: yes
csl: ["csl/bmj.csl"]
#Download your specific csl file and refer to it in the line above.
lot: true
lof: true
space_between_paragraphs: true
#Delete the # at the beginning of the previous line if you'd like
#to have a blank new line between each paragraph
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}

>>>>

---
author: 'Samuel Abbott'
date: 'August 2019'
division: 'Bristol Medical School\: Population Health Sciences'
advisor: 'Ellen Brooks Pollock'
altadvisor: 'Hannah Christensen'
department: 'Faculty of Health Sciences'
title: 'Modelling BCG vaccination in the UK'
subtitle: 'What is the impact of changing policy?'
wordcount: "55,287"
knit: "bookdown::render_book"
site: "bookdown::bookdown_site"
always_allow_html: yes
output: 
  ##Thesis can only be fully built for pdf using the makefile
  #thesisdown::thesis_pdf: default
  thesisdown::thesis_gitbook: default
  #thesisdown::thesis_word: default
  #thesisdown::thesis_epub: default
bibliography: ["bib/thesis.bib"]
#Download your specific bibliography database file and refer to it in the line above.
link-citations: yes
colorlinks: yes
csl: ["csl/bmj.csl"]
#Download your specific csl file and refer to it in the line above.
lot: true
lof: true
space_between_paragraphs: true
#Delete the # at the beginning of the previous line if you'd like
#to have a blank new line between each paragraph
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
